Medical Concept Extraction

### 2012-12-16 paper/paper.tex

\begin{figure}[t]
\begin{center}
\begin{center}
	\begin{tabular}{|l|l|}
	\hline
	\multicolumn{2}{|c|}{\bf Testing Data Set} \\ \hline
	{\bf Label} & {\bf Count}  \\ \hline
	test & 17237 \\ \hline
	none & 202438 \\ \hline
	 problem & 30276 \\ \hline
	 treatment & 17298 \\ \hline
	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{|l|l|}
	\hline
	\multicolumn{2}{|c|}{\bf Training Data Set} \\ \hline
	{\bf Label} & {\bf Count}  \\ \hline
	test & 8492 \\ \hline
	none & 114783 \\ \hline
	 problem & 17326 \\ \hline
	 treatment & 8940 \\ \hline
	\end{tabular}
\end{center}
\end{center}
\caption{The number of each class the in testing and training data sets.}
\label{fig:data_set_counts}
\end{figure}

@@

The overall size of the data was 10mb and came from Boston-area hospitals and is subject to data use agreements. The training data consisted of 170 medical records and the test data consisted of 256 medical records. Further, the distribution over labels of the training and test sets is provided in:

>>>>

\begin{figure}[t]
\begin{center}
\begin{center}
	\begin{tabular}{|l|l|l|}
	\hline
	\multicolumn{3}{|c|}{\bf Training Data Set} \\ \hline
	{\bf Label} & {\bf Count} & {\bf Percentage} \\ \hline
	test & 8492 & 5.7\\ \hline
	none & 114783 & 76.7\\ \hline
	 problem & 17326 & 11.6\\ \hline
	 treatment & 8940 & 6.0\\ \hline
	 {\bf Total} & 149541 & 100\\ \hline
	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{|l|l|l|}
	\hline
	\multicolumn{3}{|c|}{\bf Testing Data Set} \\ \hline
	{\bf Label} & {\bf Count} & {\bf Percentage} \\ \hline
	test & 17237 & 6.4\\ \hline
	none & 202438 & 75.8\\ \hline
	 problem & 30276 & 11.3\\ \hline
	 treatment & 17298 & 6.5\\ \hline
	 {\bf Total} & 267249 & 100\\ \hline
	\end{tabular}
\end{center}
\end{center}
\caption{The number of each class the in testing and training data sets.}
\label{fig:data_set_counts}
\end{figure}

@@

The overall size of the data was 10mb and came from Boston-area hospitals and is subject to data use agreements. The training data consisted of 170 medical records and the test data consisted of 256 medical records. Further, the distribution over labels of the training and test sets is provided in Figure~\ref{fig:data_set_counts}.
